State of the Practice for Medical Imaging Software

### 2022-10-27 StateOfPractice/Papers/MedImageSoft_SOP-arXiv/MedImageSoft_SOP.tex
Minor edits to threats to validity section

Below we categorize and list the threats to validity that we have identified.
Our categories come from an analysis of software engineering secondary studies
by \citet{AmpatzoglouEtAl2019}, where a secondary study analyzes the data from a
set of primary studies.  \citet{AmpatzoglouEtAl2019} is appropriate because a
common example of a secondary study is a systematic literature review. Our
methodology is a systematic software review --- the primary studies
are the software packages, and our work collects and analyzes these primary
studies.

@@

A study is reliable if its data and analysis are independent of the specific
researcher(s) doing the study.  That is, repetition of the study by a different
researcher should achieve the same results, as long as they use the same
methodology \citep{RunesonAndHost2009}.  For our study the identified
reliability related threats include the following:

\begin{itemize}
\item In our methodology, one individual does the manual measures for all
packages. The grader's abilities, experiences, and biases may influence the
results.  
\item Completing the manual measures of all packages took place over several
months. During this time the contents of the software repositories may change
and the reviewer's judgment may drift.
\end{itemize}

\begin{itemize}
\item The grading template included an entry for the reviewer's impression.  We
aimed for objectivity, but there is a risk that some scores may be subjective
and biased.
\item The measurements are made at an instant in time, and the instant differs
by a few weeks between projects, due to the time needed to measure them. For the
most part, the projects are living and continually changing, which means if we
measured at a different time, our results may change.
\end{itemize}

We investigated the risk of reviewer dependence in previous work \citep{SmithEtAl2016}, % DOUBLE BLIND
where we demonstrated that the measurement process is
reasonably reproducible by having five products graded by a second reviewer. The
ranking via this independent review was almost identical to the original
ranking. As long as each grader uses consistent definitions, the relative
comparisons in the AHP results will be consistent between graders.

>>>>

Below we categorize and list the threats to validity that we have identified.
Our categories come from an analysis of software engineering secondary studies
by \citet{AmpatzoglouEtAl2019}, where a secondary study analyzes the data from a
set of primary studies.  \citet{AmpatzoglouEtAl2019} is appropriate because a
common example of a secondary study is a systematic literature review. Our
methodology is a systematic software review --- the primary studies
are the software packages, and our work collects and analyzes these primary
studies.  \citep{SmithEtAl2022}.  \wss{add citation to LBM paper}

@@

A study is reliable if repetition of the study by different researchers using
the original study's methodology would lead to the same results
\citep{RunesonAndHost2009}. Reliability means that data and analysis are
independent of the specific researcher(s) doing the study.  For the current
study the identified reliability related threats are as follows:

\begin{itemize}
\item One individual does the manual measures for all packages. A different
evaluator might yield different results, due to differences in abilities,
experiences, and biases.
\item The manual measurements for the full set of packages took several months.
Over this time the software repositories may have changed and the reviewer's
judgment may have drifted.
\end{itemize}

We investigated the reliability risk associated with the reviewer's judgement was investigated in previous work
\citep{SmithEtAl2016}, % DOUBLE BLIND
where we demonstrated that the measurement process is
reasonably reproducible by having five products graded by a second reviewer. The
ranking via this independent review was almost identical to the original
ranking. As long as each grader uses consistent definitions, the relative
comparisons in the AHP results will be consistent between graders.
